\chapter{Reason for developing Testbench}
\label{ch:reasontestbenchdevelopment}
As shown in chapter~\ref{ch:selenium} Selenium is a powerful tool for web
testing.
However if we use Selenium to test Vaadin application we will run into several problems.

Selenium does not know about Vaadin specific features, like client-side	communication. 
Vaadin is a stateful framework - an event on a client side my affect a state of
the applicaton on a server side. This brings additional complexity in testing,
because client-side and server-side states should be synchronized.

When event happens on the client side it will notify the server side. If this event affects the server side state, the
server side will notify the client side about this change.
 Because of a network delay or long time code execution on the server side,
 there might be a delay between client side action and the change on a client. 
 In these circumstances the client-side should wait for server side code to execute,
  because it might affect the next client side instruction. To handle this
  situation we need to add a delay in a Selenium test, see line 20
   in listing~\ref{lst:seleniumVaadin}. Rely on a delay in a test is a bad
   practise, because small delay might be not enough to all client server
   communications to proceed. Adding big delay on the contrary, will increase
   the test time execution. 
   
 Because Selenium framework is not related to Vaadin it requires additional
   code to take into account client-server communication. For example setting
   value of the text field requires three lines of code instead of one see lines
   25-28 in listing~\ref{lst:seleniumVaadin}.
   
   Due to these implications a test tool for Vaadin called TestBench was
   created. TestBench is based on Selenium WebDriver, but it solves
   problems with client server communication, and brings more suitable
   API for working with Vaadin components. For example same test written with 
   the help of TestBench takes less code and does not have delays see example~\ref{lst:testbenchVaadin}.
  	
  	
  	\lstset{style=a1listing}
  	\begin{lstlisting} [caption=Selenium test for Vaadin application,label={lst:seleniumVaadin}]
public class AppTest extends TestCase{
	WebDriver driver;
    String UIUrl, nodeURL;	
	@Override @Before
    public void setUp() {
        UIUrl = "http://demo.vaadin.com/dashboard/";
        driver = new FirefoxDriver();

    }

    @Test
    public void testWithoutTestbench() {
        driver.get(UIUrl);
        driver.manage().timeouts().implicitlyWait(5, TimeUnit.SECONDS);
        List<WebElement> elements = driver.findElements(By
                .className("v-button"));
        if (elements.isEmpty()) {
            throw new RuntimeException("No buttons found");
        }
        elements.get(0).click();
        driver.findElement(By.id("dashboard-edit")).click();
        WebElement searchField = driver.findElements(By.className("v-textfield")).get(0);
        searchField.clear();
        searchField.sendKeys("New Dashboard");
        searchField.sendKeys(Keys.TAB);
        WebElement searchButton = findButtonByCaption("Save");
        searchButton.click();
        driver.manage().timeouts().implicitlyWait(5, TimeUnit.SECONDS);
        String title = driver.findElement(By.id("dashboard-title")).getText();
        Assert.assertEquals("New Dashboard", title);
    }

    public WebElement findButtonByCaption(String caption) {
        List<WebElement> buttons = driver
                .findElements(By.className("v-button"));
        for (WebElement button : buttons) {
            if (button.getText().equals(caption)) {
                return button;
            }

        }
        return null;
    }

    public WebElement findButtonByCaption(WebElement parent, String caption) {
        List<WebElement> buttons = parent
                .findElements(By.className("v-button"));
        for (WebElement button : buttons) {
            if (button.getText().equals(caption)) {
                return button;
            }

        }
        return null;
    }

    @After
    public void afterTest() {
        driver.quit();
    }
}
\end{lstlisting}

	
	\ref{lst:testbenchVaadin}.
	\lstset{style=a1listing}
  	\begin{lstlisting} [caption=TestBench test,label={lst:testbenchVaadin}]
public class TestBenchTest extends TestBenchTestCase {

    WebDriver driver;
    String UIUrl, nodeURL;

    @Before
    public void setUp() throws Exception {
        UIUrl = "http://demo.vaadin.com/dashboard/";
        setDriver(new FirefoxDriver());
    }

    @Test
    public void test1() {
        getDriver().get(UIUrl);
        $(ButtonElement.class).first().click();
        $(ButtonElement.class).id("dashboard-edit").click();
        TextFieldElement searchField = $(TextFieldElement.class).first();
        searchField.setValue("New dashboard");
        $(ButtonElement.class).caption("Save").first().click();

        String title = $(LabelElement.class).id("dashboard-title").getText();
        Assert.assertEquals("New dashboard", title);
    }

    @After
    public void afterTest() {
        // driver.quit();
    }
}  	
\end{lstlisting}